Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-07-15 paper/paperv3.qmd
H3 binom conf int

# Summarize the raw data
sexrat_summ <- pup_sex_data %>% 
  group_by(age) %>% 
  summarize(n_observed = n(), 
            n_male = sum(is_male),
            perc_male = n_male / n_observed, 
            male_lwr = binom.test()
            se = (perc_male * (1 - perc_male) / n_observed)^0.5) %>% 
  filter(age <= 20)

@@

ggplot(sexrat_pred, aes(age, predicted)) +
  # Individual years
  geom_line(aes(group = interaction(age_cat, year_fct)),
            sexrat_years,
            alpha = 0.1) +
  # Weighted model (confidence interval and mean response)
  geom_ribbon(aes(fill = age_cat, ymin = conf_lo, ymax = conf_hi), 
              alpha = 0.2) +
  geom_line(aes(color = age_cat, group = age_cat),
            linetype = "dashed", linewidth = 1.2) +
  # Population-level mean response
  geom_line(aes(y = predicted_pop, group = age_cat),
            linetype = "dotted", linewidth = 1.2, alpha = 0.5) +
  # Raw data
  geom_pointrange(aes(y = perc_male, 
                      ymin = perc_male - se, 
                      ymax = perc_male + se),
                  sexrat_summ) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Male offspring", labels = scales::percent) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  labs(x = "Age (years)") +
  theme(legend.position = "none") +
  geom_text(aes(label = n, y = .95))

>>>>

# Summarize the raw data
sexrat_summ <- pup_sex_data %>% 
  group_by(age) %>% 
  summarize(n_observed = n(), 
            n_male = sum(is_male),
            perc_male = n_male / n_observed, 
            male_lwr = binom.test(n_male, n_observed)$conf.int[1], 
            male_upr = binom.test(n_male, n_observed)$conf.int[2]) %>% 
  filter(age <= 20)

@@

ggplot(sexrat_pred, aes(age, predicted)) +
  # Individual years
  geom_line(aes(group = interaction(age_cat, year_fct)),
            sexrat_years,
            alpha = 0.1) +
  # Weighted model (confidence interval and mean response)
  geom_ribbon(aes(fill = age_cat, ymin = conf_lo, ymax = conf_hi), 
              alpha = 0.2) +
  geom_line(aes(color = age_cat, group = age_cat),
            linetype = "dashed", linewidth = 1.2) +
  # Population-level mean response
  geom_line(aes(y = predicted_pop, group = age_cat),
            linetype = "dotted", linewidth = 1.2, alpha = 0.5) +
  # Raw data
  geom_pointrange(aes(y = perc_male, 
                      ymin = male_lwr, 
                      ymax = male_upr),
                  sexrat_summ) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Male offspring", 
                     labels = scales::percent,
                     limits = c(NA, 0.97)) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  labs(x = "Age (years)") +
  theme(legend.position = "none") +
  geom_text(aes(label = n), y = .97, vjust = 0)
